The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
p2

### 2

Sociality / multilayer have been used with habitat selection and space use
... examples

Fortin 2009 showed that "bison selection of habitat and landscape features was mediated
by social group size, hypothesizing the predation risk avoidance is the strongest driver of habitat selection"

Banks 2007 habitat fragmentation influences + increased mate availability given increased home range overlap when resource availability was higher

mcloughlin2000 variable response bears to habitat quality and space use/home range overlap

>>>>

### 2
<!--
* multilayer networks are new but folks have looked at habitat selection + sociality
  * Fortin
  * Banks
  * McLoughlin

* none use a multilayer framework to explicitly combine
-->

Despite not in a multilayer network context, the link between habitat and
sociality has been previously investigated. Fortin et al. (2009) evaluated
habitat selection and group formation and division in bison. They observed
contrasting group sizes in meadows and forests as well as identified predation
risk avoidance as a main factor in their habitat selection [@Fortin_2009]. A
review of the influence of habitat fragmentation on sociality noted decreased
group size in small patches compared to large, continuous landscapes
[@Banks_2007]. Finally, McLoughlin (2000) showed variable responses in brown
bears (*Ursus arctos*) to seasonality, a proxy in this case for habitat quality,
showing high home range overlap in areas of low and high seasonality and low
home range overlap in areas of moderate seasonality. Despite these, *missing
multilayer approach*.
